---
title: "p8105_hw5_yz4717"
author: "Yang Zhao - yz4717"
date: "2023-11-12"
output: 
  html_document:
    toc: TRUE
---

```{r}
library(tidyverse)
library(ggplot2)

set.seed(1)
```

# Problem 1

```{r}
homicide_data_raw = read_csv("homicide-data.csv")
```

The raw data consist `r ncol(homicide_data_raw)` variables and `r nrow(homicide_data_raw)` observations. Each observation includes uid, reported date, victim first and last name, race, age, sex, city, state, lat, lon, and disposition.

```{r}
homicide_data = 
homicide_data_raw |>
  mutate(city_state = paste(city, state, sep=", "),
         disposition = case_match(
           disposition,
           "Closed by arrest" ~ "homicides",
           "Closed without arrest" ~ "unsolved homicides",
           "Open/No arrest" ~ "unsolved homicides"
         )) |>
  group_by(city_state, disposition) |>
  summarize(n = n()) |>
  filter(city_state != "Tulsa, AL") 
```

Tulsa, AL in city_state is removed, as it is not a major US city.

```{r}
# prop.test
homicide_data_Bal = homicide_data |>
  pivot_wider(
    names_from = "disposition", 
    values_from = "n") |>
  filter(city_state == "Baltimore, MD")

prop_test_Bal = 
  prop.test(pull(homicide_data_Bal, `unsolved homicides`), 
            pull(homicide_data_Bal, homicides) + pull(homicide_data_Bal,`unsolved homicides`))

prop_test_Bal |>
  broom::tidy() |>
  select(estimate, conf.low, conf.high)
```

```{r}
# prop.test for each city
homicide_data_prop = homicide_data |>
  pivot_wider(
    names_from = "disposition", 
    values_from = "n") |>
    filter(city_state != "Tulsa, AL") 

prop_test_city_state = function(a) {
    x = homicide_data_prop |>
      filter(city_state == a)
    
    test = prop.test(pull(x, `unsolved homicides`),
                     pull(x, homicides) + pull(x,`unsolved homicides`))
    test_result = test |>
      broom::tidy() |>
      select(estimate, conf.low, conf.high)
    
    test_result
}

test_res  = 
  data.frame(city_state = unique(pull(homicide_data_prop, city_state))) |>
  mutate(prop_test_res = purrr::map(city_state,prop_test_city_state)) |>
  unnest(cols = c(prop_test_res))
```


plot of the estimates and CIs for each city

```{r}
test_res |>
  mutate(city_state = fct_reorder(city_state, estimate)) |>
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

The plot arrange the estimate of the proportion of unsolved homicides in city,state. Chicago has the highest estimate and small range of confidence interval.

## Question 2

```{r q2_import, message=FALSE}

q2_filenames = 
  list.files(path = "data",pattern = ".csv")

q2_path = file.path("data",q2_filenames)
combined_data = NULL

data_q2 = tibble(
  source = q2_filenames,
  tibble = map(q2_path, read_csv)
) |> 
  unnest(tibble) |> 
  mutate(source = str_replace(source,".csv","")) |> 
  separate(source, into = c("arm","subject_id"), sep = "_") |> 
  relocate(arm,subject_id)

```

```{r q2_cleaned}
data_q2 |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value"
  ) |> 
  mutate(week = str_replace(week,"week_",""),
         arm = case_match(arm,
                          "con" ~ "control",
                          "exp" ~ "experiment"))|> 
  ggplot(aes(x = week, y = value,
             group = subject_id, 
             color = subject_id))+
  geom_point()+
  geom_line()+
  labs(title = " Spaghetti Plot ",
       x = "Week",
       y = "Value",
       color = "Group")+
  facet_grid(arm~.)
  
```

## Question 3

```{r q3_function}
mu = 0
sigma = 5
observations = 30
num_datasets = 5000

normtest = function(observations = 30,mu = 0,sigma = 5){
  sample = rnorm(n=observations,mean = mu,sd = sigma)
  result = t.test(sample,alternative = "two.sided",conf.level = .95) |> 
    broom::tidy() |> 
    select(estimate,p.value)
  return(result)
}

```


```{r q3_power_plot}
test_result = data_frame()
final_result = list(length = 7)

for (a in 0:6) {
  test_result = NULL
  for(i in 1:num_datasets){
  test_result = rbind(test_result,normtest(mu = a))
  }
  final_result[[a+1]] = test_result
}

power = as.vector(
  map(final_result, \(x) sum(x$p.value<.05)/5000) |> 
  unlist())
power_eff = tibble(power,effect_size = c(0:6))

power_eff |>
  ggplot(aes(x = effect_size, y = power)) +
  geom_point() +
  geom_line() +
  labs(title = "Effect Size & Power",
       x = "Effect Size",
       y = "Power") + 
  theme_minimal()

```

```{r}

mean_est = 
  as.vector(
  map(final_result,\(x) mean(x$estimate)) |> 
    unlist()
)

ave_and_true = 
  data.frame(mean_est,mu = 0:6)

ave_and_true |>
  ggplot(aes(x = mu,
             y = mean_est)) +
  geom_point(color = "yellow") +
  geom_line(color = "yellow") +
  labs(title = "Average Estimate & True Mean",
       x = "True Mean",
       y = "Average Estimate") 

```


```{r}
reject_true = lapply(final_result,function(df){
   filtered = df |> 
     filter(df$p.value<.05)
   return(mean(filtered$estimate))
}) |> 
  unlist()
  
rej_true_df = 
  data.frame(reject_true,
             true_mean = 0:6)

ggplot() +
  geom_point(data = ave_and_true,
             aes(x = mu, y = mean_est),
             color = "red") +
  geom_line(data = ave_and_true,
            aes(x = mu, y = mean_est),
            color = "red") +
  geom_point(data = rej_true_df,
             aes(x = true_mean, y = reject_true),
             color = "blue") +
  geom_line(data = rej_true_df,
            aes(x = true_mean, y = reject_true),
            color = "blue") +
  labs(title = "Average Estimate vs. True Mean",
       x = "True Mean",
       y = "Average Estimate")
```

